\section{Introduction}
\subsection{What is Functional Programming?}
Functional programming is a programming paradigm that focuses on treating computations as the evaluation of pure functions. These functions are characterized by two key properties:

\begin{itemize}
    \item \textbf{Pure Functions}: They always produce the same output for the same set of inputs, regardless of external factors or the program's state. They don't produce side effects, meaning they don't modify existing data or have unintended consequences outside their scope.
    \item \textbf{Immutability}: Functional programming emphasizes working with immutable data structures. This means data cannot be changed after creation, promoting a more predictable and easier to reason about program state.
\end{itemize}

In contrast to imperative programming, which focuses on how to achieve a result through a sequence of statements, functional programming emphasizes what the result should be. This leads to a more declarative style of coding, where you describe the desired outcome rather than the specific steps to achieve it.

\subsection{Functional Programming in Python}
While Python is primarily an imperative language, it offers a rich set of features and libraries that enable functional programming techniques. This report will explore how to leverage these features to write code that adheres to functional principles.

We'll also examine popular functional programming libraries in Python, such as \texttt{functools} and \texttt{itertools}, which provide additional tools and utilities for writing functional code.

By understanding and applying these concepts, you can enhance your Python code by making it:

\begin{itemize}
    \item \textbf{More Concise}: Functional programming often leads to more compact and readable code.
    \item \textbf{More Modular}: Functions become well-defined units of logic, promoting reusability and maintainability.
    \item \textbf{More Testable}: Pure functions with no side effects are easier to test and isolate for verification.
\end{itemize}

This report will equip you with the knowledge to leverage functional programming principles within Python, leading to more robust and elegant solutions.
